Wikipedia Text Mining and Entropy Analysis

### 2019-03-01 wiki_entropy/wiki_clustering.Rmd
starting on WALS imputation & MCA

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(missMDA)
library(cluster)
library(widyr)
library(lsa)
library(magrittr)
library(broom)
library(here)
library(feather)

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(missMDA)
library(cluster)
library(widyr)
library(lsa)
library(magrittr)
library(broom)
library(here)
library(feather)
library(FactoMineR)

@@

```{r imputation and MCA}
wiki_gs <- gs_title("Wikipedia_absolute")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

# Phonology `1A`:`19A`
# Morphology `20A`:`29A`
# Nominal Categories `30A`:`57A`
# Nominal Syntax `58A`:64A`
# Verbal syntax `65A`:`80A`
# Word order `81A`:`97A`, `143A`, `144A`
# Simple clauses `98A`:`120A`
# Complex sentences `121A`:`128A`
# Lexicon `129A`:`138A`
# Sign languages `139A`:`140A`

phon_wf <- wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode) %>%
  select(`1A`:`19A`, language)

phon_wf <- phon_wf[rowSums(is.na(phon_wf)) < 15,]
```
